\hiddenchapter{\large{Committee Descriptions}}
\ChapterTitle[\thechapter]{Committee Descriptions}
\renewcommand{\thesection}{\textbf{C-\arabic{section}}}

\hiddensection{\large{Arts Committee}}
\SectionTitle{\thesection}{Arts Committee}
\begin{enumerate}
    \item Arts Committee consists of an Arts Chair who is elected at a JCR Meeting and other interested members.
    \item Arts Committee will be in charge of organising an Arts Week once a year for College.
    \item Arts Committee is responsible for promoting the arts and organising arts-related activities around College.
\end{enumerate}

\hiddensection{\large{Ball Committee}}
\SectionTitle{\thesection}{Ball Committee}

\begin{enumerate}
    \item Ball Committee is responsible for the organisation and financial management of the Winter Ball and Summer Ball. They will endeavour to provide a suitable event which reflects the interests of the entire College.
    \item There shall be a separate Ball Committee for both the Winter and Summer Ball.
    \item Ball Committee consists of the Ball Chair(s), Ball Committee Representatives who have volunteered to be involved and the JCR President.
    \item A Ball Chair is elected before each ball at a JCR meeting to serve for that event.
\end{enumerate}


\hiddensection{\large{Butler Day Committee}}
\SectionTitle{\thesection}{Butler Day Committee}

\begin{enumerate}
    \item Butler Day Committee is responsible for the organisation and financial management of Butler Day. Butler Day is the official ‘College Day’ where all common rooms are invited to celebrate the culmination of the academic year. This will take place within the last three weeks of Easter Term.
    \item Butler Day Committee consists of the Butler Day Chair, the Social Chair, Butler Day Committee Representatives who have volunteered to be involved and the JCR President
    \item A Butler Day Chair is elected at a JCR meeting to serve for that event.
\end{enumerate}


\hiddensection{\large{Butler Talks Committee}}
\SectionTitle{\thesection}{Butler Talks Committee}

\begin{enumerate}
    \item Butler Talks Committee, chaired by the Butler Talks Chair(s), is responsible for organising and ensuring the smooth running of a Butler Talks events which will suitably reflect the interests of the JCR, providing a platform for sharing ideas and giving voice to different topics and perspectives.
    \item The committee will promote the event to find suitable entertainment and select appropriate speakers for the event, including but not limited to JCR members as well as members of the wider community when suitable.
    \item The committee will work with members of the JCR as well as faculty members of Josephine Butler College in order to ensure the smooth running of the event.
    \item The committee can consist of as many members as are interested, with the Butler Talks Chair(s) responsible for advertising the committee to JCR members. The Vice President will also act in an advisory capacity to the committee.
\end{enumerate}

\hiddensection{\large{Charity Committee}}
\SectionTitle{\thesection}{Charity Committee}

\begin{enumerate}
    \item There shall be a Charity Committee consisting of the following members.
    \begin{enumerate}
        \item The Charity Comm Chair who shall chair the Committee as well as attend central DUCK committee meetings and training.
        \item Assistant Charity Co-ordinator elected at a Charity Committee Meeting as an internal, who shall provide support for the Charity Co-ordinator(s) and deputise in their absence. The Assistant Charity Co-ordinator(s) shall also be responsible for organising rag raids in conjunction with central DUCK and promoting all charity related events and projects both within the college and the wider community in connection with Publicity Committee and the Vice President.
        \item The Vice President, responsible for minuting the meeting, or delegating the task where appropriate.
    \end{enumerate}
    \item The Charity Committee shall have the following duties:
    \begin{enumerate}
        \item To be responsible for organising and implementing all charity fund-raising events in College including College events during DUCK week/Charities Week.
        \item To be responsible for the promotion of events organised by DUCK, as well as local and national charity events, and encouraging members of the JCR to participate in them.
        \item To assist individuals from the JCR wishing to host fundraising or charity events.
        \item To allow the elected Charity Coordinators and the Charity Committee to choose which charities are supported in college and decide how the money raised is allocated to these charities
    \end{enumerate}
    \item There shall be one Assistant Charities Coordinator who will aid the Charities Coordinator(s) in the carrying out of their roles and responsibilities, will be elected within the Charity committee as an internal role and shall:
    \begin{enumerate}
        \item Assist the Charities Coordinators in the undertaking of their role. 
        \item Assist with the planning, organisation and setting up of charity events. 
        \item Attend all meetings of Charities Committee.
        \item Encourage the involvement of all college members in special charity events.
    \end{enumerate}
    \item The Charity Committee Treasurer will aid the Charities Coordinator(s) and Assistant Charities Coordinator in the carrying out of their roles and responsibilities, acting as an assistant with a focus on the financial aspects of the committee. They will be elected within Charity Committee as an internal role and shall:
    \begin{enumerate}
        \item Assist the Charities Coordinators in the undertaking of their role. 
        \item Always ensure the safe storage of cash fundraised by the committee.
        \item Attend all meetings of Charities Committee.
        \item Maintain financial records for the committee.
    \end{enumerate}
\end{enumerate}

\hiddensection{\large{Democracy Committee}}
\SectionTitle{\thesection}{Democracy Committee}

\begin{enumerate}
    \item Membership of the Democracy Committee consists of the JCR Chair and three vice-chairs.
    \item Democracy Committee shall meet at least weekly for the purposes of checking all minutes taken by vice-chairs since the last meeting of Democracy Committee.
    \item All members of Democracy Committee cannot vote in any decision in which they are acting in their capacity as Chair or Vice-chair.
    \item The only exception is the case of a tie (excluding Executive Committee elections, see OS 5.3.2), in which the Chair will cast the deciding vote.
\end{enumerate}



\hiddensection{\large{DSU Committee}}
\SectionTitle{\thesection}{DSU Committee}

\begin{enumerate}
    \item DSU Committee shall be attended by the JCR President, JCR Vice-President, DSU Rep, and Assistant DSU Rep, along with any interested JCR or MCR members.
    \item The Committee shall discuss DSU and NUS matters and provide support to the DSU Rep to help them fulfil their role as outlined in C-2.1.
    \item The Committee shall be held before every SU Assembly, following the release of the Assembly papers.
    \item The Assistant DSU Rep shall be elected within DSU Committee as in internal role and shall:
    \begin{enumerate}
        \item Attend Assembly with the DSU Rep and provide advice and assistance where needed. 
        \item Help promote campaigns in college.
        \item Deputise the DSU Rep when they are unable to perform their role.
    \end{enumerate}
    \item If the current DSU Rep is an undergraduate, there shall be one Assistant DSU Rep who is a postgraduate and one that is an undergraduate. If the DSU rep is a postgraduate, there shall be two Assistant DSU reps who are undergraduates and none who are postgraduates.
\end{enumerate}


\hiddensection{\large{Equality and Diversity Committee}}
\SectionTitle{\thesection}{Equality and Diversity Committee}

\begin{enumerate}

    \item The Equality and Diversity Committee shall conduct a vote of committee members to determine who should perform the roles of chair, and secretary. This election is held at the first meeting of each academic year. However, the chair of the committee reserves the right to call an election at any other point.
    \item The Committee will be composed of a minimum of the Welfare Officer, JCR President, FACSO, JCR Chair, International Officer, Students with Disabilities Rep, LGBT+ Gender Identity Rep, LGBT+ Orientation Rep, MCR Welfare Officer, MCR International Rep. Any other member of the JCR may also be a member. All members, except the JCR Chair, will have a vote within the committee.
    \item The Committee will take action to promote, and address, any issues or proposals that relate to equality or diversity, within the college community.
    \item The Committee will meet at least once per term, to discuss specific proposals, which are submitted to the committee’s chair and secretary prior to the meeting.
\end{enumerate}


\hiddensection{\large{Fashion Show Committee}}
\SectionTitle{\thesection}{Fashion Show Committee}

\begin{enumerate}
    \item Fashion Show Committee, chaired by the Fashion Show Chair(s), is/are responsible for organising and ensuring the smooth running of a Fashion Show which will suitably reflect the interests of the JCR.
    \item The committee can consist of as many members as are interested, with the Social Chair responsible for advertising the committee to JCR members. The Social Chair will also act in an advisory capacity to the committee.
\end{enumerate}


\hiddensection{\large{Finance Committee}}
\SectionTitle{\thesection}{Finance Committee}

\begin{enumerate}
    \item The role of Finance Committee is to ensure the JCR account is monitored suitably, ensure fair allocation of budgets to clubs, societies, committees and any other JCR members who have access to funds within the JCR account (these groups shall hence forth be referred to ‘budget holders’) and ensure any use of JCR money is appropriate.
    \item The voting membership consists of the Treasurer, President, Sports Officer, Societies Officer, Social Chair, MCR Treasurer, JCR Vice President, and FACSO as elected at a JCR meeting.
    \item Decisions will be made by a straight majority and in the event of a tie the Chair shall cast the deciding vote.
    \item The minutes shall be done by a Vice Chair and chaired by the JCR Chair.
    \item (Current/Potential) Budget holders can apply to Finance Committee for funding. Applications must state their current financial position, the reason for the application and amount, other sources of income and a breakdown of projected expenditure for the year in which funding is being applied for.
    \item (Current/Potential) Budget holders that submit funding applications are then able to attend the relevant Finance Committee meeting to support their application and answer any questions relating to it.
    \item Finance Committee can request a thorough breakdown of all expenditures and incomes (excluding any money acquired through fundraising; see C-4.10.9) of budget holders that receive funding before it can be put to use. This is in order to maintain transparency, fair play and ensure appropriate use of JCR funds. This request cannot be refused without good cause.
    \item It is beyond the mandate of finance comm. to force a budget holder to spend their money in a particular way. However, finance comm. may deem planned expenditure of a budget holder as inappropriate use of JCR funds and insist on the budget holder returning with an alternative. It must be clearly stated in the minutes why this decision was made.
    \item Any money acquired through fundraising specifically for an asset for the budget holder (and by extension the JCR) must be used to purchase such an asset. It is beyond the mandate for finance comm. to suggest otherwise, although, finance comm. may choose to turn down such money if its source would damage the image of the JCR. Finance comm. should be informed of fundraising taking place to uphold transparency. (Note: membership income in the case of clubs and societies cannot be considered fundraised money).
    \item The committee may ask a relevant treasurer/responsible officer to explain any anomalies within the accounts. In the case of malpractice, a Question of Officer (and if desired a Vote of No Confidence) may be submitted.
    \item All decisions of finance comm. are subject to usual appeals process through a further finance comm. meeting, executive committee or a JCR meeting.
\end{enumerate}


\hiddensection{\large{Freshers' Week Committee}}
\SectionTitle{\thesection}{Freshers' Week Committee}

\begin{enumerate}
    \item There shall be a Freshers’ Week Committee consisting of the Head Frep(s) (who shall chair the committee), the Freps (who shall be appointed during Easter Term), the President, the President- elect, the International Officer and the Chilled Frep.
    \item The function of the Freshers’ Week Committee shall be to assist the Head Frep(s) in the organisation and smooth running of Freshers’ Week.
    \item Freshers Week is a week of events and activities designed to introduce Freshers to Josephine Butler College, Durham University and Durham City. Activities must reflect the diverging interests of potential Freshers so that all feel comfortable and encouraged to take part in the opportunities presented to them. The week must also espouse a sense of ‘Butler Sprit’ amongst Freshers.
    \item The Committee shall meet during the Easter term to co-ordinate Freshers Week. They shall also meet immediately prior to the start of Freshers’ Week to make final arrangements.
    \item During the summer vacation, the Head Frep(s) and JCR President shall be in regular contact and be able to make decisions on behalf of the Committee, although the JCR Treasurer may be consulted on financial matters.
\end{enumerate}


\hiddensection{\large{Green Committee}}
\SectionTitle{\thesection}{Green Committee}

\begin{enumerate}
    \item Green Committee consists of the Vice President, Green Committee Rep, and as many members as are interested. Meetings will be chaired by the Green Committee Rep and the Vice President shall take minutes.
    \item Green committee shall work to Lead the JCR environmental effort, and to help the College in the realisation of its objective of being a green College. This can be achieved by:
    \begin{enumerate}
        \item Increasing awareness of environmental issues within the JCR through regular campaigns, events and other communication methods.
        \item Promoting positive environmental behavioural change amongst the College community.
        \item Facilitate Greenspace events which are appropriate to Butler College.
    \end{enumerate}
    \item Duties of Green Committee members include devising, implementing, managing and appraising green initiatives on a College, and potentially University level; and working with the Operational Facilities Manager to help implement green policies and practices within the College.
    \item The Assistant Green Committee Rep(s), as an individual or a pair, shall be elected within a Green Committee Meeting as an internal role and shall:
    \begin{enumerate}
        \item Assist the Green Rep in the undertaking of their role.
        \item Attend all meetings of Green Committee.
        \item Encourage the involvement of all College members in green events.
    \end{enumerate}
\end{enumerate}


\hiddensection{\large{Gym Committee}}
\SectionTitle{\thesection}{Gym Committee}

\begin{enumerate}
    \item Howlands Farm Gym Committee consists of the President, Sports Officer and one Gym Rep elected at a JCR General Meeting; and the President, Treasurer, Secretary and two Gym Reps appointed by the JCR from Stephenson College.
    \item Butler’s Sports Officer is the de facto Facilities Manager for the Gym.
    \item Duties should include;
    \begin{enumerate}
        \item Ensuring the effective, fair and safe day to day management and administration of the gym.
        \item Working alongside the Operational Facilities Manager of Josephine Butler College in exercising these duties;
        \item Helping to advertise the gym to new members;
        \item Ensure the smooth recruitment of new members including registration of new members’ details, the collection of new members’ fees and the appropriate induction of new members;
        \item Ensure that proper accounts are kept;
        \item Act as treasurers in the allocation and administration of gym funds;
        \item Act as a disciplinary committee in the event of acts of transgression against the gym Code of Conduct.
    \end{enumerate}
    \item The Committee shall adhere to the Howlands Farm Gym Management Policy.
\end{enumerate}

\hiddensection{\large{International Committee}}
\SectionTitle{\thesection}{International Committee}

\begin{enumerate}
    \item International Committee consists of the International Officer and as many members as are interested.
    \item International Committee shall work to:
    \begin{enumerate}
        \item Project internationalisation positively throughout college life by organising a wide range of cultural activities.
        \item Strive for internationalisation of college, involving both home and international students in projects that aim to celebrate and expose cultural diversity.
        \item Help international students get as involved as possible in college life, working alongside existing committees, sports and societies.
        \item Recognise some specific needs of international students, and help to support them wherever possible. Shall seek to provide practical support throughout their time at Durham acting as a point of contact for any questions or concerns.
        \item Support Erasmus students with their specific needs and requirements, taking into account the fact that they arrive at different points and stay for varying lengths of time.
    \end{enumerate}
    \item There shall be two Assistant International Officers elected within the committee as internal roles, who shall:
    \begin{enumerate}
        \item Assist the International Officer in the undertaking of their role.
        \item Promote diversity in college and seek to encourage International engagement.
        \item Support the International Officer in creating/organising events such as International Festival.
        \item Be present during freshers’ week as a representative of international committee. 
        \item Be entitled to an automatic interview to become a full member of the frep team.
    \end{enumerate}
\end{enumerate}

\hiddensection{\large{JBs Committee}}
\SectionTitle{\thesection}{JBs Committee}

\begin{enumerate}
    \item  JB’s Committee consists of the Bar Steward and Food Services Officer as Co-Chairs and all JB’s staff as members.
    \item The purpose of the JBs committee is to ensure that all staff members have a say in the workings of the bar and coffee shop; promote the bar and coffee shop; to discuss any issues or problems the staff have.
    \item The Assistant Food Services Officer shall be elected within JB’s Committee as an internal role and shall:
    \begin{enumerate}
        \item Assist the Food Services Officer in the undertaking of their role.
        \item Be a point of contact for staff on shift who have any queries or concerns.
        \item Help with the maintenance of the social media presence of JB’s, via the Facebook, Instagram, and other social networks.
        \item Undertake a minimum of 4 shifts per term working in accordance with the food staff job descriptions.
        \item Support the JCR Food Services Officer with the organisation and promotion of bar events.
        \item Offer ideas, suggestions and recommendations to the JCR Food Services Officer which will help to develop JB’s.
    \end{enumerate}
\end{enumerate}

\hiddensection{\large{Livers in Proctor Committee}}
\SectionTitle{\thesection}{Livers in Proctor Committee}

\begin{enumerate}
    \item Appointment to the Committee is achieved through an interview and is selected by the JCR President in conjunction with the Welfare Officer.
    \item Livers In Proctors are responsible for:
    \begin{enumerate}
        \item Providing two-way feedback to the JCR President.
        \item Attending weekly Proctor meetings.
        \item Acting as a point of contact for all Livers In.
        \item Signposting students to the appropriate welfare provisions where necessary. 
        \item Distributing publicity material.
        \item Encourage participation in College events.
    \end{enumerate}
\end{enumerate}


\hiddensection{\large{Livers Out Committee}}
\SectionTitle{\thesection}{Livers Out Committee}

\begin{enumerate}
    \item Livers Out Committee is responsible for ensuring that the JCR members that live outside of college accommodation are kept involved as much as possible within the college community. It is also their responsibility to ensure the welfare provision of livers out is of a high standard and any issues arising are dealt with quickly and efficiently.
    \item Membership of the Livers Out Committee consists of the Head Livers Out Rep, the Welfare Officer, and the Livers Out Reps. The JCR President will be invited (at the discretion of the Head Livers Out Rep) if it is deemed appropriate.
    \item ivers Out Reps are appointed through an interview panel, on which the JCR President and Head Livers Out Rep shall preside.
    \item Each Livers Out Rep is responsible for a group of houses containing Butler students and shall act as an impartial link between the house, college and the JCR.
    \item Each Livers Out Rep is required to have contact with each of their areas a minimum of three times a term where possible. It is the duty of the Head Livers out Rep to ensure this is being fulfilled.
    \item One member of the committee (not the Welfare Officer) is required to attend the fortnightly Livers In Proctor meetings and to act as an intermediary between the two.
    \item The committee is responsible for organising and running the find a house campaign. It is the duty of the Head Livers Out Rep to ensure support and advice is given all year through not just over the house hunting period. The committee is also responsible for assisting the Head Livers Out Rep in his role as required: this may include attending Livers In Proctor meetings and attending DSU Livers Out meetings.
\end{enumerate}



\hiddensection{\large{Mound Committee}}
\SectionTitle{\thesection}{Mound Committee}

\begin{enumerate}
    \item Mound Committee consists of a Mound Editor who is elected by the JCR at a General Meeting and as many members as are interested.
    \item Mound Committee is to produce Mound magazine.
    \item Mound exists to provide a well-rounded overview of college life which is accessible to all of its members. The format should be inviting and readable.
    \item It shall be free of charge to members of college. If printing costs are deemed too much by Finance Committee, then sponsorship and advertisement should be sought.
    \item Duties of members include contributing and editing content; and assisting with the printing and distribution of the magazine. Specific editorial positions will be assigned to individual members to help the editorial process.
    \item As an individual or a pair, the deputy mound editor(s) shall be elected within the mound committee as an internal role and shall:
    \begin{enumerate}
        \item Support the Mound Editor in encouraging a wide variety of students to write articles for the magazine.
        \item Support the Mound Editor in promoting readership of Mound Magazine. 
        \item There shall be up to two deputy mound editors, as one individual, or a pair
    \end{enumerate}
\end{enumerate}

\hiddensection{\large{Music Committee}}
\SectionTitle{\thesection}{Music Committee}

\begin{enumerate}
    \item Music Committee must be attended by the Music Committee Chair(s), a representative from all music societies and the Technical Directors. It is also open to any JCR member.
    \item The committee will assist the Music Committee Chair(s) in the undertaking of their role, specifically in the organisation, setting up and management of live music events in the college.
    \item The Committee will also look to discover and promote wider external music events, be it those at other colleges, those held in independent institutions, or even large events outside Durham, for all those interested. In some cases, this responsibility will extend to organising trips and encouraging attendance.
    \item Elected roles within the committee are Live Music Coordinator, Music Publicity Coordinator, Music Committee Assistant Chair, and Music Outreach Officer. If these positions are not filled the Music Committee Chair(s) must perform these roles themselves.
    \begin{enumerate}
        \item Live music coordinator shall:
        \begin{enumerate}
            \item Be responsible for the organisation and financial management of live music events at the college, specifically, but not limited to, Open Mic Nights and Butler Live.
            \item Organise and Chair Live Music Committee, consisting of the Technical Directors and any members of the JCR who wish to join.
            \item Look to discover and promote wider music events beyond the college, be it those at other colleges, those held in independent institutions, or even large events outside Durham, for all those interested. In some cases, this responsibility will extend to organising trips and encouraging attendance.
            \item Liaise closely with existing music-based societies who may have special knowledge of events and bands from their own experience.
        \end{enumerate}
        \item Music Publicity Coordinator shall:
        \begin{enumerate}
            \item Promote all music events at Butler via social media and making posters and circulating them.
        \end{enumerate}
        \item Music Committee Assistant Chair shall:
        \begin{enumerate}
            \item Minute all Music Committee meetings. 
            \item Assistant the Music Committee Chair(s) in their role.
        \end{enumerate}
        \item Music Outreach Officer shall:
        \begin{enumerate}
            \item  Find performance opportunities for groups and individuals within the JCR outside of Butler.
            \item Coordinate volunteering opportunities for musicians and music groups within the JCR.
        \end{enumerate}
    \end{enumerate}
\end{enumerate}


\hiddensection{\large{Photography Committee}}
\SectionTitle{\thesection}{Photography Committee}

\begin{enumerate}
    \item Photography Committee consists of the Photography Director, who will chair the meetings, the Publicity Officer, and as many members as are interested.
    \item Photography Committee is to work alongside Publicity Committee: to publicise JCR events, assisting in the creation of promotional content and the coverage of events; to provide a forum for discussion between photographers; to actively encourage the engagement of new members.
    \item The Photography Committee Chair is responsible for organising tutorial sessions for beginners to encourage new membership and oversee the smooth running of the committee.
\end{enumerate}

\hiddensection{\large{Publicity Committee}}
\SectionTitle{\thesection}{Publicity Committee}

\begin{enumerate}
    \item Publicity Committee consists of the Publicity Officer, who will chair the meetings, and as many members as are interested.
    \item The aim of publicity committee is to assist JCR committees, societies and clubs to publicise events, activities and other such matters.
    \item Duties of Publicity Committee should include designing relevant publicity items to meet the specified aims and objectives of the requester; and to maintain a workable and manageable publicity liaison system in which a clear policy exists that allows for easy requests/ response to be made to/ from the committee.
    \item The Publicity Officer is responsible for organising tutorial sessions for beginners to encourage new membership and to oversee the smooth running of the committee.
    \item The Assistant Publicity Officer shall be elected internally in Publicity Committee as an internal role
    and shall:
    \begin{enumerate}
        \item Assist the Publicity Officer in the undertaking of their role.
        \item Hold a strong knowledge of Adobe Photoshop and Illustrator packages. 
        \item Promote Publicity Committee within College, actively encouraging participation.
    \end{enumerate}
\end{enumerate}

\hiddensection{\large{Social Committee}}
\SectionTitle{\thesection}{Social Committee}

\begin{enumerate}
    \item Social Committee consists of the Social Chair and as many co-opted members as are interested.
    \item Social Committee shall discuss, assist and lead where necessary the organisation of JCR social events whilst also taking into account the financial implications. They shall also help promote the advertisement of these events.
    \item There shall be four Assistant Social Chairs who will aid the Social Chair in the carrying out of their roles and responsibilities. They will be elected internally by social committee as internal roles and shall:
    \begin{enumerate}
        \item Assist the Social Chair in the undertaking of their role.
        \item Attend Social Committee.
        \item Promote social events within college and actively encourage participation.
        \item Support the Social Chair in creating/organising events such as formals, Newcastle Nights Out and other assorted JCR excursions.
        \item Be present during freshers’ week as a representative of social committee.
        \item Be entitled to an automatic interview to become a full member of the frep team.
    \end{enumerate}
   
\end{enumerate}


\hiddensection{\large{Societies Committee}}
\SectionTitle{\thesection}{Societies Committee}

\begin{enumerate}
    \item Societies Committee consists of the Societies Officer as the chair and the society presidents.
    \item The purpose of the Societies Committee is to ensure that all societies are running properly and democratically; promote the benefits of college engagement; to discuss any issues or problems the presidents have; to promote collaboration between societies.
    \item There shall be two Assistant Societies Officers elected within societies committee as internal roles, who shall:
    \begin{enumerate}
        \item Assist the Societies Officer in the undertaking of their role.
        \item Promote societies within College, and actively encourage participation.
        \item Support the Societies Officer in creating/organising events such as Butler Fair and Societies Showcase.
        \item Be in charge of a Societies section of the Sports and Societies Week in the calendar.
        \item Coordinate society creation up to ratification. \item Help compile termly reports of going on in societies. 
        \item Help to run AGMs for any societies who need assistance.
    \end{enumerate}
\end{enumerate}


\hiddensection{\large{Sports Captain's Committee}}
\SectionTitle{\thesection}{Sports Captain's Committee}

\begin{enumerate}
    \item The purpose of the Captain’s Committee is to ensure that all clubs are running properly and democratically; promote the benefits of college sport; to discuss any issues or problems either the captains or the sporting officers have; to keep the Captains up to date with DUAU (Team Durham); to keep good links between all of the teams; and ensure teams are constantly promoting the active engagement of new members.
    \item Captains Committee will meet at least once a term.
    \item The two Assistant Sports Officers shall be elected as an internal role in Sports Captain’s Committee and will be responsible for supporting the Sports Officer throughout the year. This includes:
    \begin{enumerate}
        \item Helping to develop sport within Butler.
        \item Organising and promoting sporting events within College
        \item Encouraging the involvement of all College members in Butler sport.
    \end{enumerate}

\end{enumerate}


\hiddensection{\large{Technical Committee}}
\SectionTitle{\thesection}{Technical Committee}

\begin{enumerate}
    \item Technical Committee consists of the Technical Director(s) (as elected at a JCR meeting) who will chair meetings, and co-opted members.
    \item Technical Committee is to liaise and assist any member of the JCR with technical requirements associated with JCR business.
    \item Technical Committee members must also attend any relevant training.
\end{enumerate}

\hiddensection{\large{Volunteering Committee}}
\SectionTitle{\thesection}{Volunteering Committee}

\begin{enumerate}
    \item  Volunteering Committee consists of the Vice President, who will chair the meetings, the Volunteer Rep, the respective Project Leaders, and as many members as are interested.
    \item The Committee should devise, implement and manage JCR projects, especially those related to the local community.
    \item The Duties should include identifying suitable JCR projects; devising the relevant areas of the projects; ensuring the effective management of the scheme including the recruitment and supervision of appropriate volunteers; helping to promote and encourage awareness of JCR projects.
    \item The Intergenerational Project Leader shall be elected within the Volunteering Committee as an internal role and shall:
    \begin{enumerate}
        \item Run the Intergenerational Project with the help of the Volunteer Rep, Vice President, and College Chaplain
        \item Attend every planning meeting and the bi-weekly events organised by Intergenerational Project
        \item Be responsible for publicising all events and trying to get more people involved
    \end{enumerate}
    \item The RT Projects Leader shall be elected within Volunteering Committee as an internal role and shall:
    \begin{enumerate}
        \item Run the RT Project with the help of the Volunteer Rep, Vice President, and the College Chaplain
        \item Attend every planning meeting and event organised by the RT Committee 
        \item Be responsible for publicising all events and trying to get more people involved.
    \end{enumerate}
\end{enumerate}


\hiddensection{\large{Welfare Committee}}
\SectionTitle{\thesection}{Welfare Committee}

\begin{enumerate}
    \item Welfare Committee must be attended by the Welfare Officers, Assistant Welfare Officers, and the JCR President when required. It is also open to any JCR member.
\end{enumerate}